InformatiCup 2024 Ctrl-Alt-Defeat

### 2023-12-19 paper.tex
First report and references for Stable diffusion

\subsubsection{Image generating models}

>>>>

\subsubsection{Image generating models}
The first image generating model we us is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.
